Supporting Information:\n prolfqua - A Comprehensive R-package for Proteomics Differential Expression Analysis

### 2022-10-22 inst/MyArticle/prolfqua_supplement.Rmd
cleanup

tmp <- dplyr::bind_rows(proda, prolfqua)
tmp$what |> unique()
tmp$what[tmp$what == "statistic"] <- "t_statistic"
tmp$what[tmp$what == "scaled.pval"] <- "scaled.p.value"
tmp <- tmp |> filter(contrast == "all")
```

>>>>

tmp <- dplyr::bind_rows(proda, prolfqua)
tmp$what[tmp$what == "statistic"] <- "t_statistic"
tmp$what[tmp$what == "scaled.pval"] <- "scaled.p.value"
tmp <- tmp |> filter(contrast == "all")
```
